Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-12-13 paper.tex
Added VIP importer and applications descriptions

Until recently, applications were integrated in VIP as workflows defined and managed 
with the MOTEUR\cite{GLAT-08} workflow engine. As of today, Boutiques is supported 
through a "Boutiques application importer" tool allowing to automatically import
applications based on their JSON description.

\todo{Sorina, Tristan: develop on the functionalities and current limits of the application importer?}

@@

\todo{Sorina, a paragraph on other applications in VIP?}

>>>>

Until recently, applications were manually integrated in VIP as workflows written 
in the Gwendia\cite{MONT-09} language and managed  with the MOTEUR\cite{GLAT-08} workflow engine. 
As of today, Boutiques is supported through a "Boutiques application importer" tool, which 
parses the JSON file and automatically generates the corresponding application workflow
and the wrapper script that handles, among others, the execution of the command line itself. 
The use of an application workflow allows to (i) iterate on input lists and generate 
parallel tasks, as well as to (ii) concatenate multiple tools. The applications used in 
the MICCAI challenges, for example, were followed by other tool allowing to compute 
challenge-specific metrics. Tool concatenation is currently handeled at the importer 
level based on pre-defined workflow templates.

\todo{Tristan: validate the description above}

@@

\paragraph{VIP applications.}A few tools were imported in VIP using Boutiques.

The first one is a phase contrast simulator called CreaPhase and developed at Creatis. 
The CreaPhase inputs had certain particularies (some nedeed to be enclosed 
in simple quotes, other were vectors of variable size enclosed in brackets)
that required the post-processing of the wrapper script generated by the
Boutiques importer.

The Odin MRI simulator\footnote{\url{http://od1n.sourceforge.net}} was also imported 
in VIP using Boutiques. Since Odin  may require important amounts of computing resources 
(the common use-case consists in iterating on a large number of inputs files), Odin is 
executed by VIP on the EGI grid resources, which currently do not support Docker. Consequently, 
the Odin executable was exported from the Docker image which allowed for his CentOS compilation
and the Odin wrapper script was modified so that it makes no "Docker run" call.

A few MRtrix3\footnote{\url{http://www.mrtrix.org/}} tools were also make available in VIP. 
A script developed at Creatis, which combines MRtrix3 and FSL tools, is currently being
imported and tested.

\todo{Tristan: validate the descriptions above}
